---
title: Antibiotics in PHCs and MCs
subtitle: "Analyzing supplies of antibiotics from June to December against the data extracted from HMIS"
date: "01, February 2023"
author: "Dr. Zyad Ejjilat<br>Abdullah Almohammed"
format: 
  revealjs:
    auto-stretch: false
    preview-links: true
    slide-number: true
    logo: images/Medecins-sans-frontieres-logo-MSF.png
    #footer: "IDAL's PHC and MC Antibiotics report"
    css: styles.css
    navigation-mode: vertical
    controls: true
    controls-layout: bottom-right
    controls-tutorial: true 
    touch: true
    institute: "MSF - OCBA"
    output-file: "IDAL_presentation"
    fig-align: center
    fig-width: 10
    fig-height: 6 
    transition: slide
    background-transition: fade
    #scrollable: true
  
embed-resources: true
---

# Data Processing

## Isystock data

::: incremental
-   Export all Isystock's movement
-   Filter only regular donation
-   Prepare list of all Antibiotic + Paracetamol + Ibuprofen (PHC and MC Sentinel)
-   Fetch the [WHO DDD](https://www.whocc.no/atc_ddd_index/) for each item, and each AB category[(Access, Watch)](https://aware.essentialmeds.org/list)
:::

## Isystock data

::: incremental
-   Look up the minimum and maximum treatment period accord. to MSF[^1]
-   Take the average period and define the quantities per course for each item
-   Join both Isystock's extracted data and the Sentinel list data, now we get only data of interest.
-   Calculate number of courses of each item by dividing the donated quantity by the number of units per course.
:::

[^1]: from both Clinical guidelines and Essential Medicines

## HMIS Data

::: incremental
-   Export HMIS data for all health facilities (HF) for concerned period.
-   **Age**:
    -   Under 5 years U5.
    -   Over 5 years O5.
-   **consultation categories**:
    -   Total consultations.
:::

## HMIS data processing

::: incremental
-   harmonize HF names with Isystock.
-   calculate the total number of consultation for each Age category.
-   Merge both processed data and start the Analysis.
:::

# Access vs Watch AB

```{r}
#| include: false

library(tidyverse)
library(plotly)
library(purrr)
library(glue)
library(lubridate)
library(kableExtra)
library(here)
library(xlsx)

access_lst <-
read.xlsx(
  here("std/antibiotics.xlsx"),
  sheetName = "PHC"
) %>%
mutate(
  Age = if_else(is_it_more_than_5== "TRUE", "5 years or more", "Under 5 years"),
  unit_per_course = rounded_course
) %>%
select(
  Code, Article, DDD, U, AWaRe, Age, rounded_course
) %>%
filter(
  AWaRe == "Access"
)
watch_lst <-
read.xlsx(
  here("std/antibiotics.xlsx"),
  sheetName = "PHC"
) %>%
mutate(
  Age = if_else(is_it_more_than_5== "TRUE", "5 years or more", "Under 5 years"),
  unit_per_course = rounded_course
) %>%
select(
  Code, Article, DDD, U, AWaRe, Age, rounded_course
) %>%
filter(
  AWaRe == "Watch"
)

```

## Access group antibiotics

This group includes antibiotics that have activity **against a wide range of commonly encountered susceptible pathogens** while also showing **lower resistance potential** than antibiotics in the other groups. <br>Selected Access group antibiotics are recommended as **essential first or second choice empiric treatment options for infectious syndromes**.

## 

```{r}
access_lst %>% kbl() %>%
 kable_styling(
   bootstrap_options = c("striped", "hover", "condensed"),
   font_size = 15,
   html_font = "Cambria"
     )
```

## Watch group antibiotics

This group includes antibiotic classes that have **higher resistance potential** and includes most of the highest priority agents among the **Critically Important Antimicrobials for Human** Medicine and/or antibiotics that are at relatively high risk of selection of bacterial resistance. These medicines should be prioritized as key targets of stewardship programs and monitoring. <br>Selected Watch group antibiotics are recommended as essential first or second choice empiric treatment options for a limited number of specific infectious syndromes.

## 

```{r}
watch_lst %>% kbl() %>%
 kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
               font_size = 16,
               html_font = "Cambria")
```

## 

here we will analyze the supply of medication regardless of consultation data for each facility per age group per month.

this ratio should be in favor of Access group \>60% according to WHO *"The WHO General Program of Work 2019-2023 has adopted a new indicator based on AWARE: Access \>60%"* [^2]

[^2]: from AWaRe Policy Brief [here is the document.](https://adoptaware.org/assets/pdf/aware_policy_brief.pdf)

```{r}

```

```{r}
#| include: false
source(here("code/04_read_IDAL_processed_data.R"))
source(here("code/05_Abdullahlib.R"))

idal_course_isy <-
  idal_course_isy %>% 
  filter(
    unite_dest != "Mental Health Activity" &
      unite_dest != "INH CCTC"
    ) 

HFs <- unique(idal_course_isy$unite_dest)



    
adult <- 
  HFs %>%
    map(
      .f = plot_access_watch,
      df = idal_course_isy,
      age_cat = TRUE
      )
paed <- 
   HFs %>%
    map(
      .f = plot_access_watch,
      df = idal_course_isy,
      age_cat = FALSE
      )

```

## 

```{r}
#| fig-cap: "Total AB trend is steady state between (2000 - 2550) course."
#| fig-subcap: "September and April are out of target."

adult[[1]] %>% 
  add_ribbons(
    x = 0:13, 
    ymin = 2000, 
    ymax = 2550, 
    name = "SS", 
    hoverinfo = "none",
    showlegend = FALSE
    ) %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "August, October, November and December are out of target."
#| fig-cap: "The percentage of Watch is increasing toward end of year" 
paed[[1]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "Within target except for July."
#| fig-cap: "Total AB is in steady state around (800-1000) courses."

adult[[3]] %>% 
  add_ribbons(
    x = 0:13, 
    ymin = 800, 
    ymax = 1000, 
    name = "SS", 
    hoverinfo = "none",
    showlegend = FALSE
    ) %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-cap: "Most of months the ratios are equal (maybe they prescribe the second option in 50% cases)"
#| fig-subcap: "Total AB is in steady state around (440-550) courses."
paed[[3]] %>% 
  add_ribbons(
    x = 0:13, 
    ymin = 440, 
    ymax = 550, 
    name = "SS", 
    hoverinfo = "none",
    showlegend = FALSE
    ) %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "February, April, May, June and December are out of target."
#| fig-cap: "Total AB is in steady state around (650-810) courses."
adult[[4]] %>% 
  add_ribbons(
    x = 0:13, 
    ymin = 650, 
    ymax = 810, 
    name = "SS", 
    hoverinfo = "none",
    showlegend = FALSE
    ) %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
paed[[4]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-cap: "Supply was not stable to infer anything"
adult[[6]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-cap: "Supply was not stable to infer anything"
paed[[6]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-cap: "out of target except for November and December."
adult[[5]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-cap: "After May we almost did not provide them with Watch group, WHY?"
paed[[5]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "The ratio is good"
#| fig-cap: "There is downtrend over last year of supply of all Antibiotics."
adult[[9]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "What about November and December? (was it closed?)"
#| fig-cap: "It is out of target (they tends to prescribe second choices for paed.)"
paed[[9]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "Good ratio"
adult[[8]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "Almost perfect ratio."
paed[[8]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
adult[[10]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
paed[[10]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "Out of target most of the months."
adult[[7]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
paed[[7]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

# Percentage of AB prescription to consultation

```{r}
#| include: false


xx <-
  idal_course_isy %>% 
  inner_join(
    .,
    idal_hmis,
    by = c("unite_dest" = "unit")
    ) 

HF <- unique(xx$unite_dest) 
remove(xx)

ab_cns_adlt <- 
  HF %>%
    map(
      .f = plot_AB_consult,
      df_isy = idal_course_isy,
      df_hmis = idal_hmis,
      age_cat = TRUE
      )
ab_cns_pd <- 
   HF %>%
    map(
      .f = plot_AB_consult,
      df_isy = idal_course_isy,
      df_hmis = idal_hmis,
      age_cat = FALSE
      )

```

## 

```{r}
ab_cns_adlt[[1]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_pd[[1]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_adlt[[3]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_pd[[3]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_adlt[[5]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_pd[[5]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_adlt[[6]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_pd[[6]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_adlt[[7]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_pd[[7]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_adlt[[8]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_pd[[8]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_adlt[[3]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_pd[[3]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_adlt[[2]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_pd[[2]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

# Observation & Recommendations

## Observations:

::: incremental
1.  In general, there is a high rate of antibiotics consumption, this is even higher in **mobile activities and pediatric consultations**.
2.  In some facilities, the number of Abx courses delivered is higher than the number of consultations. This needs investigation, beginning from assumptions about consultation registration in HMIS to Abx prescription habits.  
3.  Overall, there is a high tendency to prescribe the Watch antibiotics group for pediatrics in all HFs. 
4.  The ratio of antipyretic/analgesics to antibiotics is unexpected, this is especially true for Under 5 Years patients. 
:::

## Recommendations:
::: incremental
1.  Investigate the practices for the HFs with higher ratio AB courses/consultations: reporting/inventory related issues could impact the analysis.
2. Emphasize on the importance of respecting protocols and guidelines (fight against AB resistance, stock management: avoid shortage…).
3. Syrup presentation should be kept in priority for small kids, less than 2 years old.
4. Promote the use of new presentation: children, dispersible…
:::


<!-- ```{r} -->
<!-- # ab_admn_adlt <-  -->
<!-- #   HF %>% -->
<!-- #     map( -->
<!-- #       .f = plot_AB_admn_consult, -->
<!-- #       df_isy = idal_course_isy, -->
<!-- #       df_hmis = idal_hmis, -->
<!-- #       age_cat = TRUE -->
<!-- #       ) -->
<!-- # ab_admn_pd <-  -->
<!-- #    HF %>% -->
<!-- #     map( -->
<!-- #       .f = plot_AB_admn_consult, -->
<!-- #       df_isy = idal_course_isy, -->
<!-- #       df_hmis = idal_hmis, -->
<!-- #       age_cat = FALSE -->
<!-- #       ) -->

<!-- ``` -->

<!-- # plot atc levet 3 -->

<!-- ```{r} -->

<!-- atc3_lst <- unique(sentinel_list$atc_3) -->

<!-- atc_adlt <- -->

<!--   HF %>% -->

<!--     map( -->

<!--       .f = atc3_plot, -->

<!--       df_isy = idal_course_isy, -->

<!--       age_cat = TRUE -->

<!--       ) -->

<!-- atc_pd <- -->

<!--    HF %>% -->

<!--     map( -->

<!--       .f = atc3_plot, -->

<!--       df_isy = idal_course_isy, -->

<!--       age_cat = FALSE -->

<!--       ) -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_adlt[[1]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_pd[[1]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_adlt[[2]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_pd[[2]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_adlt[[3]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_pd[[3]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_adlt[[4]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_pd[[4]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_adlt[[5]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_pd[[5]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_adlt[[6]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_pd[[6]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_adlt[[7]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_pd[[7]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_adlt[[8]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_pd[[8]] -->

<!-- ``` -->
