---
title: Antibiotics in PHCs and MCs
subtitle: "Analyzing supplies of antibiotics from June to December against the data extracted from HMIS"
date: "01, February 2023"
author: "Dr. Zyad Ejjilat<br>Abdullah Almohammed"
format: 
  revealjs:
    auto-stretch: false
    preview-links: true
    slide-number: true
    logo: images/Medecins-sans-frontieres-logo-MSF.png
    #footer: "NAP's PHC and MC Antibiotics report"
    css: styles.css
    navigation-mode: vertical
    controls: true
    controls-layout: bottom-right
    controls-tutorial: true 
    touch: true
    institute: "MSF - OCBA"
    output-file: "NAP_PHC_MC_AB_presentation"
    fig-align: center
    fig-width: 10
    fig-height: 6 
    transition: slide
    background-transition: fade
    #scrollable: true
  
embed-resources: true
---

# Data Processing

## Isystock data

::: incremental
-   Export all Isystock's movement
-   Filter only regular donation
-   Prepare list of all Antibiotic + Paracetamol + Ibuprofen (PHC and MC Sentinel)
-   Fetch the [WHO DDD](https://www.whocc.no/atc_ddd_index/) for each item, and each AB category[(Access, Watch)](https://aware.essentialmeds.org/list)
:::

## Isystock data

::: incremental
-   Look up the minimum and maximum treatment period accord. to MSF[^1]
-   Take the average period and define the quantities per course for each item
-   Join both Isystock's extracted data and the Sentinel list data, now we get only data of interest.
-   Calculate number of courses of each item by dividing the donated quantity by the number of units per course.
:::

[^1]: from both Clinical guidelines and Essential Medicines

## HMIS Data

::: incremental
-   Export HMIS data for all health facilities (HF) for concerned period.
-   **Age**:
    -   Under 5 years U5.
    -   Over 5 years O5.
-   **consultation categories**:
    -   Total consultations.
:::

## HMIS data processing

::: incremental
-   harmonize HF names with Isystock.
-   calculate the total number of consultation for each Age category.
-   Merge both processed data and start the Analysis.
:::

# Access vs Watch AB

```{r}
#| include: false

library(tidyverse)
library(plotly)
library(purrr)
library(glue)
library(lubridate)
library(kableExtra)
library(here)
library(xlsx)

access_lst <-
read.xlsx(
  here("std/antibiotics.xlsx"),
  sheetName = "PHC"
) %>%
mutate(
  Age = if_else(is_it_more_than_5== "TRUE", "5 years or more", "Under 5 years"),
  unit_per_course = rounded_course
) %>%
select(
  Code, Article, DDD, U, AWaRe, Age, rounded_course
) %>%
filter(
  AWaRe == "Access"
)
watch_lst <-
read.xlsx(
  here("std/antibiotics.xlsx"),
  sheetName = "PHC"
) %>%
mutate(
  Age = if_else(is_it_more_than_5== "TRUE", "5 years or more", "Under 5 years"),
  unit_per_course = rounded_course
) %>%
select(
  Code, Article, DDD, U, AWaRe, Age, rounded_course
) %>%
filter(
  AWaRe == "Watch"
)

```

## Access group antibiotics

This group includes antibiotics that have activity **against a wide range of commonly encountered susceptible pathogens** while also showing **lower resistance potential** than antibiotics in the other groups. <br>Selected Access group antibiotics are recommended as **essential first or second choice empiric treatment options for infectious syndromes**.

## 

```{r}
access_lst %>% kbl() %>%
 kable_styling(
   bootstrap_options = c("striped", "hover", "condensed"),
   font_size = 15,
   html_font = "Cambria"
     )
```

## Watch group antibiotics

This group includes antibiotic classes that have **higher resistance potential** and includes most of the highest priority agents among the **Critically Important Antimicrobials for Human** Medicine and/or antibiotics that are at relatively high risk of selection of bacterial resistance. These medicines should be prioritized as key targets of stewardship programs and monitoring. <br>Selected Watch group antibiotics are recommended as essential first or second choice empiric treatment options for a limited number of specific infectious syndromes.

## 

```{r}
watch_lst %>% kbl() %>%
 kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
               font_size = 16,
               html_font = "Cambria")
```

## 

here we will analyze the supply of medication regardless of consultation data for each facility per age group per month.

this ratio should be in favor of Access group \>60% according to WHO *"The WHO General Program of Work 2019-2023 has adopted a new indicator based on AWARE: Access \>60%"* [^2]

[^2]: from AWaRe Policy Brief [here is the document.](https://adoptaware.org/assets/pdf/aware_policy_brief.pdf)


```{r}
#| include: false
source(here("code/06_read_NAP_processed_data.R"))
source(here("code/05_Abdullahlib.R"))

nap_course_isy <-
  nap_course_isy %>% 
  filter(
    unite_dest != "Mental Health Activity" &
      unite_dest != "INH CCTC"
    ) 

HFs <- unique(nap_course_isy$unite_dest)



    
adult <- 
  HFs %>%
    map(
      .f = plot_access_watch,
      df = nap_course_isy,
      age_cat = TRUE
      )
paed <- 
   HFs %>%
    map(
      .f = plot_access_watch,
      df = nap_course_isy,
      age_cat = FALSE
      )

```

## 

```{r}
#| fig-cap: "..."
#| fig-subcap: "..."

adult[[1]] %>%
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "..."
#| fig-cap: "..." 
paed[[1]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "...."
#| fig-cap: "..."

adult[[2]] %>%  
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-cap: "..."
#| fig-subcap: "..."
paed[[2]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "...."
#| fig-cap: "...."
adult[[3]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
paed[[3]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-cap: "..."
adult[[4]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-cap: "..."
paed[[4]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-cap: "...."
adult[[5]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-cap: "..."
paed[[5]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "..."
#| fig-cap: "..."
adult[[6]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "..."
#| fig-cap: "...."
paed[[6]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "..."
adult[[7]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "..."
paed[[7]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
adult[[8]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
paed[[8]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

# Percentage of AB prescription to consultation

```{r}
#| include: false


xx <-
  nap_course_isy %>% 
  inner_join(
    .,
    nap_hmis,
    by = c("unite_dest" = "unit")
    ) 

HF <- unique(xx$unite_dest) 
remove(xx)

ab_cns_adlt <- 
  HF %>%
    map(
      .f = plot_AB_consult,
      df_isy = nap_course_isy,
      df_hmis = nap_hmis,
      age_cat = TRUE
      )
ab_cns_pd <- 
   HF %>%
    map(
      .f = plot_AB_consult,
      df_isy = nap_course_isy,
      df_hmis = nap_hmis,
      age_cat = FALSE
      )

```

## 

```{r}
ab_cns_adlt[[1]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_pd[[1]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_adlt[[2]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_pd[[2]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_adlt[[3]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_pd[[3]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_adlt[[4]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```


## 

```{r}
ab_cns_adlt[[5]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_pd[[5]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_adlt[[6]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_pd[[6]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_adlt[[7]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
ab_cns_pd[[7]] %>% 
  layout(
    legend = list(
      x= 0.6,
      y=0.95,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```


# Observation & Recommendations

## Observations:

<!-- ::: incremental -->
<!-- 1.  there is decline over all last year in supply **(ISH Mat, Termanin PHC)** -->
<!-- 2.  there is high tendency to prescribe **Watch** group antibiotic for **pediatrics** in all HFs. -->
<!-- 3.  in general there is high rate of Antibiotics consumption especially in **mobile activities**. -->
<!-- 4.  unexpected ratio of antipyretics & analgesics to antibiotics for Under 5 Years patients. -->
<!-- 5.  there is a problem in each facility we supply it with 100% AB for age category and needs more investigations. -->
<!-- ::: -->

## Recommendations:
<!-- ::: incremental -->
<!-- 1. double check the decline overall last year supply of some facilities with consultation data and causes. -->
<!-- 2. promote Antibiotic stewardship and focus on **AWaRe categorization** and urge them to preserve the **Watch** group for children as it is more likely to develop ***antibiotic resistance***. -->
<!-- 3. investigate the reasons of over-prescribing Antibiotics with MD and pharma in the facilities, and advocate for **enhancing prescribing habits**. -->
<!-- ::: -->

<!-- ## Recommendations: -->
<!-- ::: incremental  -->
<!-- 4. check the availability of Metronidalzole 250mg tab, **Paracetamol 100mg tab and Ibuprofen 200mg tab** in all HFs and continuous supply of it. -->
<!-- 5. revise the registration process in HFs specially in mobile activity. -->
<!-- ::: -->

<!-- ```{r} -->
<!-- # ab_admn_adlt <-  -->
<!-- #   HF %>% -->
<!-- #     map( -->
<!-- #       .f = plot_AB_admn_consult, -->
<!-- #       df_isy = idal_course_isy, -->
<!-- #       df_hmis = idal_hmis, -->
<!-- #       age_cat = TRUE -->
<!-- #       ) -->
<!-- # ab_admn_pd <-  -->
<!-- #    HF %>% -->
<!-- #     map( -->
<!-- #       .f = plot_AB_admn_consult, -->
<!-- #       df_isy = idal_course_isy, -->
<!-- #       df_hmis = idal_hmis, -->
<!-- #       age_cat = FALSE -->
<!-- #       ) -->

<!-- ``` -->

<!-- # plot atc levet 3 -->

<!-- ```{r} -->

<!-- atc3_lst <- unique(sentinel_list$atc_3) -->

<!-- atc_adlt <- -->

<!--   HF %>% -->

<!--     map( -->

<!--       .f = atc3_plot, -->

<!--       df_isy = idal_course_isy, -->

<!--       age_cat = TRUE -->

<!--       ) -->

<!-- atc_pd <- -->

<!--    HF %>% -->

<!--     map( -->

<!--       .f = atc3_plot, -->

<!--       df_isy = idal_course_isy, -->

<!--       age_cat = FALSE -->

<!--       ) -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_adlt[[1]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_pd[[1]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_adlt[[2]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_pd[[2]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_adlt[[3]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_pd[[3]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_adlt[[4]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_pd[[4]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_adlt[[5]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_pd[[5]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_adlt[[6]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_pd[[6]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_adlt[[7]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_pd[[7]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_adlt[[8]] -->

<!-- ``` -->

<!-- ## -->

<!-- ```{r} -->

<!-- atc_pd[[8]] -->

<!-- ``` -->
