---
title: Antibiotics in PHCs & MCs<br>OCBA - SYRIA Mission
subtitle: "Analyzing supplies of antibiotics from June to December 2023 against the data extracted from HMIS"
date: "15, May 2023"
#author: "Dr. Zyad Ejjilat<br>Abdullah Almohammed"
format: 
  revealjs:
    auto-stretch: false
    preview-links: true
    slide-number: true
    logo: ..\images\Doctorswithoutborders.jpg
    footer: "Syria Mission's PHC and MC Antibiotics analysis"
    css: styles.css
    navigation-mode: vertical
    controls: true
    controls-layout: bottom-right
    controls-tutorial: true 
    touch: true
    institute: "MSF - OCBA - SYRIA Mission"
    output-file: "OCBA_SY_PHC_MC_AB_presentation"
    fig-align: center
    fig-width: 10
    fig-height: 6 
    transition: slide
    background-transition: fade
    #scrollable: true
  
embed-resources: true
editor: visual
---

# Context

::: incremental
1.  Armed conflict with lots of displacements
2.  Working through partnership of DoH and local NGOs (MSF is NOT the direct implementer of services).
3.  Two projects: IDAL and NAP
4.  Supporting PHCs, MCs, BEmONCs and CEmONCs
5.  Regular monthly medical donations based on the facilities consumption
6.  AMR and Antibiotics over-prescribing are quiet spread in Syria
:::

# objectives

::: incremental
1.  Evaluate the antibiotic usage:\
    is there Antibiotics over-prescribing in Facilities? where? how much? how often?
2.  Evaluate the rational prescribing behavior:\
    are first line of ABs prescribed (Access group) or skipped to second line (Watch group) immediately?
3.  Double check the balance between antipyretic courses and antibiotics courses?
:::

# Data resources

::: incremental
-   Monthly donations extracted from Isystock (it is based on the facilities monthly consumption)
-   Export HMIS data for all health facilities (HF) for concerned period.
-   **Age**:
    -   Under 5 years U5.
    -   5 years or more O5.
-   **consultation categories**:
    -   Total consultations.
:::

# Parameters

::: incremental
1.  define the Antibiotics list in the mission and its category based on WHO AWaRE categorization (Access, Watch)
2.  define Age categories of those medications:
    -   Under 5 years U5 (pediatrics: Suspension, Syrups, dispersible tablets and pediatrics injectables
    -   5 years or more O5: Tablets and injectables for adult
:::

## 

::: incremental
3.  Define the Duration of treatment based on MSF[^1] (the average duration of treatment of the main indication of the drug)
4.  [WHO DDD](https://www.whocc.no/atc_ddd_index/): Daily defined dose is the assumed average maintenance dose (grams) per day for a drug used for its main indication in adults.
5.  Calculation of number of units of medication per course
    -   Under 5 years U5:\
        each bottle of suspension or syrup are 1 course.
:::

[^1]: from both Clinical guidelines and Essential Medicines

## 

::: incremental
-   5 years or more O5:\
    DDD \* DoT / (dose of medication per unit in grams) Amoxicillin 500 mg =\>\
    DDD is 1.5 gram =\> duration of treatment is between 5 to 7 days =\>\
    7 (duration of treatment)\* 1.5 (DDD)/ 0.5 (dose of medicine per unit in grams) = 21 tablets\
    Amoxicillin 500mgcourse is 21 tablets.\
:::

## Access group antibiotics

```{r}
#| include: false

library(tidyverse)
library(plotly)
library(purrr)
library(glue)
library(lubridate)
library(kableExtra)
library(here)
library(xlsx)

access_lst <-
read.xlsx(
  here("std/antibiotics.xlsx"),
  sheetName = "PHC"
) %>%
mutate(
  Age = if_else(is_it_more_than_5== "TRUE", "5 years or more", "Under 5 years"),
  unit_per_course = rounded_course
) %>%
select(
  Code, Article, DDD, U, AWaRe, Age, unit_per_course
) %>%
filter(
  AWaRe == "Access"
)
watch_lst <-
read.xlsx(
  here("std/antibiotics.xlsx"),
  sheetName = "PHC"
) %>%
mutate(
  Age = if_else(is_it_more_than_5== "TRUE", "5 years or more", "Under 5 years"),
  unit_per_course = rounded_course
) %>%
select(
  Code, Article, DDD, U, AWaRe, Age, unit_per_course
) %>%
filter(
  AWaRe == "Watch"
)

```

```{r}
access_lst %>% kbl() %>%
 kable_styling(
   bootstrap_options = c("striped", "hover", "condensed"),
   font_size = 15,
   html_font = "Cambria"
     )
```

## Watch group antibiotics

```{r}
watch_lst %>% kbl() %>%
 kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
               font_size = 16,
               html_font = "Cambria")
```

```{r}
#| include: false
source(here("code/04_read_Mission_processed_data.R"))
source(here("code/05_Abdullahlib.R"))

sy_course_isy <-
  sy_course_isy %>% 
  filter(
    unite_dest != "Mental Health Activity" &
      unite_dest != "Staff Health"
    ) 

HFs <- unique(sy_course_isy$unite_dest)



    
adult <- 
  HFs %>%
    map(
      .f = plot_access_watch,
      df = sy_course_isy,
      age_cat = TRUE
      )
paed <- 
   HFs %>%
    map(
      .f = plot_access_watch,
      df = sy_course_isy,
      age_cat = FALSE
      )

```

```{r}
#| include: false


xx <-
  sy_course_isy %>% 
  inner_join(
    .,
    hmis,
    by = c("unite_dest" = "unit")
    ) %>%
   inner_join(
    .,
    hmis_mor,
    by = c("unite_dest" = "unit")
    )
  

HF <- unique(xx$unite_dest) 
remove(xx)

ab_cns_adlt_mor <- 
  HF %>%
    map(
      .f = plot_AB_consult_mor,
      df_isy = sy_course_isy,
      df_hmis = hmis,
      df_mor = hmis_mor,
      age_cat = TRUE
      )
ab_cns_pd_mor <- 
   HF %>%
    map(
      .f = plot_AB_consult_mor,
      df_isy = sy_course_isy,
      df_hmis = hmis,
      df_mor = hmis_mor,
      age_cat = FALSE
      )
ab_cns_adlt <- 
  HF %>%
    map(
      .f = plot_AB_consult,
      df_isy = sy_course_isy,
      df_hmis = hmis,
      age_cat = TRUE
      )
ab_cns_pd <- 
   HF %>%
    map(
      .f = plot_AB_consult,
      df_isy = sy_course_isy,
      df_hmis = hmis,
      age_cat = FALSE
      )

```

# Antibiotic Mission view

## 

```{r}
#| fig-subcap: "Mission's ratio of Access to Watch - **5 years or more**"

mission_plot_access_watch(sy_course_isy, TRUE)%>%
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )

```

## 

```{r}
#| fig-subcap: "Mission's Percentage of Antibiotics & Antipyrretics to consultations - **5 years or more**"

mission_plot_AB_consult(sy_course_isy,hmis, TRUE) %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "Mission's ratio of Access to Watch - **Under 5 years**"

mission_plot_access_watch(sy_course_isy, FALSE) %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "Mission's Percentage of Antibiotics & Antipyrretics to consultations - **Under 5 years**"


mission_plot_AB_consult(sy_course_isy,hmis, FALSE) %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

::: incremental
-   there is a downtrend in Antibiotic consumption in category 5 Years and more throughout the analysis period. (improvement)

-   the consultation rate is almost stable of category 5 years and more. (improvement)

-   the trend of antibiotic consumption of category under 5 years is stable somehow. (neutral)

-   ratio of Watch group to Access group is still high in under 5. (neutral)

-   rate of Antibiotic consumption in Under 5 years is almost double the 5 years and more. (neutral)
:::

# Access vs Watch AB

## IDAL Project view

## 

```{r}
#| fig-subcap: "steep drop in consuption of AB in last summer season the stable low consmption of AB, Accepted ratio (Access to Watch)"

adult[[2]] %>%  
  layout(
    legend = list(
      x= 0.8,
      y=1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "surge in Watch ratio (Access to Watch) since starting supporting the NICU in Dec"

paed[[2]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "decline in AB consumption (look suspiciously low in last 6 months)"

adult[[18]] %>%  
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "there is downtrend in total without any change in the ratio (Access to Watch)"

paed[[18]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "there is steep decline in AB consumption since the Earthquake in Feb"

adult[[7]] %>%  
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "steep decline in watch group since Feb (investagation is needed)"

paed[[7]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "uptrend in AB consumption with two Surges (Feb and Apr), to improve the ratio (Access to Watch)"

adult[[12]] %>%  
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "uptrend in AB consumption since Jan, the ratio (Access to Watch) needs improvement"

paed[[12]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "ratio (Access to Watch) needs improvements"

adult[[5]] %>%  
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-cap: "ratio (Access to Watch) needs improvements, **suspicioius surge in Jun**"

paed[[5]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "downtrend since Dec, good ratio (Access to Watch) also"

adult[[13]] %>%  
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "stable AB consumption and good ratio (Access to watch)"

paed[[13]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "downtrend and improvement in AB consumption and ratio (Access to Watch)"

adult[[19]] %>%  
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "decline in AB since Apr with good ratio (Access to Watch) overall"

paed[[19]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## NAP Project view

## 

```{r}
#| fig-subcap: "ratio of (Access to Watch) close to each others, two surges one in Feb EQ and the other last summer"

adult[[6]] %>%  
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "stable AB consumption with surge in Feb EQ, the ratio (Access to Watch) needs improvement"

paed[[6]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "Inverted ratio (Access to Watch), Investigate"

adult[[11]] %>%  
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "ratio (Access to Watch) needs improvements, Investage Oct surge"

adult[[14]] %>%  
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "Inverted Ratio (Access to Watch), Investage"

paed[[14]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "uptrend in watch (CLOSED)"

adult[[1]] %>%  
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "acceptable ratio (Access to Watch) (CLOSED)"

paed[[1]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "high fluctuations in AB and the ratio (Access to Watch)"

adult[[4]] %>%  
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "fluctuation in AB and ratio (Access to Watch)"

paed[[4]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "increase in watch in last three months (almost inverted ratio)"

adult[[16]] %>%  
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "acceptable ratio (Access to Watch)"

paed[[16]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "acceptable ratio (Access to Watch)"

adult[[15]] %>%  
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "acceptable ratio (Access to Watch)"

paed[[15]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "high ratio of Watch (equal)"

adult[[3]] %>%  
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-cap: "good ratio (Access to Watch)"

paed[[3]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=15, color=I("black")
        )
      )
    )
```

# Percentage of AB prescription to consultation

## IDAL project view

## 

```{r}
#| fig-subcap: "very good cooporation and response"

ab_cns_adlt[[2]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "since Jan they stoped collecting paed data only from NICU"

ab_cns_pd[[2]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "very good ratios"

ab_cns_adlt[[15]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good ratio"

ab_cns_pd[[15]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "decline in AB ratio since Feb, WHY?"

ab_cns_adlt[[7]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "high consumption of AB in winter months and less, invistgate April surge in antipyrrtic"

ab_cns_pd[[7]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "this PHC is growing in all terms (consultations and consumption)"

ab_cns_adlt[[9]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "very high consumption since March (almost evey chil is given AB and antipyretic"

ab_cns_pd[[9]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "new facility, good ratio"

ab_cns_adlt[[5]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "new facility, Investigate June data"

ab_cns_pd[[5]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "there is noticeable imporvement and still there window for more improvement"

ab_cns_adlt[[10]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "NO noticicable improvement (need strict actions)"

ab_cns_pd[[10]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "AB consumption is improving"

ab_cns_adlt[[16]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1, 
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good improvement and ther is still a window for more"

ab_cns_pd[[16]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## NAP Project view

## 

```{r}
#| fig-subcap: "good ratio"

ab_cns_adlt[[6]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good ratio"

ab_cns_pd[[6]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good ratio"

ab_cns_adlt[[8]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good ratio"

ab_cns_adlt[[11]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "unstable nr of consultaion, to check the data?"

ab_cns_pd[[11]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good ratio, CLOSED"

ab_cns_adlt[[1]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "always growing consumption, CLOSED"

ab_cns_pd[[1]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good ratio"

ab_cns_adlt[[4]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good ratio, investagate Feb surge"

ab_cns_pd[[4]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good ratio"

ab_cns_adlt[[13]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good ratio, check last months surge in antipyretics"

ab_cns_pd[[13]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good ratio"

ab_cns_adlt[[12]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "acceptable ratio, investigate last 2 months surge"

ab_cns_pd[[12]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good ratio"

ab_cns_adlt[[3]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "very high AB consumption rate"

ab_cns_pd[[3]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

# Percentage of AB prescription to infectious cases

## IDAL project view

## 

```{r}
#| fig-subcap: "very good cooporation and response"

ab_cns_adlt_mor[[2]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "since Jan they stoped collecting paed data only from NICU"

ab_cns_pd_mor[[2]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "very good ratios"

ab_cns_adlt_mor[[15]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good ratio"

ab_cns_pd_mor[[15]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "decline in AB ratio since Feb, WHY?"

ab_cns_adlt_mor[[7]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "high consumption of AB in winter months and less, invistgate April surge in antipyrrtic"

ab_cns_pd_mor[[7]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "this PHC is growing in all terms (consultations and consumption)"

ab_cns_adlt_mor[[9]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "very high consumption since March (almost evey chil is given AB and antipyretic"

ab_cns_pd_mor[[9]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "new facility, good ratio"

ab_cns_adlt_mor[[5]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "new facility, Investigate June data"

ab_cns_pd_mor[[5]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "there is noticeable imporvement and still there window for more improvement"

ab_cns_adlt_mor[[10]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "NO noticicable improvement (need strict actions)"

ab_cns_pd_mor[[10]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "AB consumption is improving"

ab_cns_adlt_mor[[16]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1, 
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good improvement and ther is still a window for more"

ab_cns_pd_mor[[16]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## NAP Project view

## 

```{r}
#| fig-subcap: "good ratio"

ab_cns_adlt_mor[[6]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good ratio"

ab_cns_pd_mor[[6]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good ratio"

ab_cns_adlt_mor[[9]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good ratio"

ab_cns_adlt_mor[[11]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "unstable nr of consultaion, to check the data?"

ab_cns_pd_mor[[11]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good ratio, CLOSED"

ab_cns_adlt_mor[[1]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "always growing consumption, CLOSED"

ab_cns_pd_mor[[1]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good ratio"

ab_cns_adlt_mor[[4]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good ratio, investagate Feb surge"

ab_cns_pd_mor[[4]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good ratio"

ab_cns_adlt_mor[[13]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good ratio, check last months surge in antipyretics"

ab_cns_pd_mor[[13]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good ratio"

ab_cns_adlt_mor[[12]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "acceptable ratio, investigate last 2 months surge"

ab_cns_pd_mor[[12]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "good ratio"

ab_cns_adlt_mor[[3]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

## 

```{r}
#| fig-subcap: "very high AB consumption rate"

ab_cns_pd_mor[[3]] %>% 
  layout(
    legend = list(
      x= 0.8,
      y= 1.1,
      xanchor='center',
      yanchor='top',
      bgcolor= 'rgba(0,0,0,0)',
      bordercolor = I("black"),
      borderwidth = 1,
      orientation = 'h',
      font=list(
        size=10, color=I("black")
        )
      )
    )
```

# Observation & Recommendations

## Observations:

::: incremental
:::

## Recommendations:

::: incremental
:::
